% Autogenerated translation of readme.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\section*{This is the advanced equipment of the TPF-TOOLS\_v1.1b for macOS 10.14+}

macOS "big sur" only Intel!

\section*{Important:}

Make sure that you have installed JackOSX!
Take the  'TPF tool JackOSX Installer.command' to do this.
If not, go to download install\_JackOSX

After the JackOSX installation, you have to restart your Macintosh. If everything went well, you should now create an aggregate. How to do this is described here:

https://support.apple.com/en-us/HT202000.

\section*{installer tpf-tool-advanced}

The 'tpf-tool-advanced' corresponds to the previous basic idea of TPF tools for eLearning the 'tpf-tool-basic' and 'tpf-tools-intermediate'.
advanced stands for modularly structured application possibilities for eLearning and Performances (simple to quite complex settings).
The most important addition is the possibility to create a 3D audio mix for headphones (binaural) as well as for speakers (ambisonics).
Audio and video are independent of each other. Ultragrid can but does not have to be used.

\section*{Download:}

tpf-tools-advanced go to GitHub: 
https://github.com/joambi/

\hrule
\section*{Install the tpf-tools-advanced:}

1.download the DMG

2.open the DMG

3.open the folder ' installer-tpf-tools-advanced'

4.right-click the 'install-tpf-tools-advanced.command'

5.enter your admin-PW

6.follow the installer instructions.

\section*{The Installer installs the following components:}

\section*{Applications:}

\begin{itemize}
\item tpf-party.app   (v1.1-beta4)	
\item tpf-client.app  (v1.1-beta5)
\item Ardour6.6.app	
\item uv-qt.app (Ultragrid 1.6+)
\end{itemize}

\section*{Scripts:}

\begin{itemize}
\item tpf-runner.command
\item tpf-save-audio.command
\item tpf-load-audio.command	
\end{itemize}

\section*{Folders:}

\begin{itemize}
\item tpf-settings 
\item tpf-basic.txt
\item tpf-audio-connections 
\item tpf-basic.xml
\item ardour-templates
\item tpf-basic.ardour
\end{itemize}

\section*{tpf-video-scripts:}

\begin{verbatim}
- video-runner-camera01.command 
- video-runner-camera02.command
- video-selftest-camera01.command
- video-selftest-camera02.command	
\end{verbatim}

\section*{tpf-uninstallers:}

\begin{verbatim}
- uninstaller-JackOSX.command
- uninstaller-tpf-tool.command
\end{verbatim}

Ambisonics \& Binaural  Audio-Plug-Ins (free) installed in:    --$>$ /Library/

\section*{Audio/Plug-Ins:}

\begin{verbatim}
- ICST Ambisonics Plugins   --> ambisonics
- dearVR_AMBI_MICRO(free)  --> binaural
- IEMPluginSuite_v1.11.1 --> reverb
\end{verbatim}

\section*{Info:}

https:/tpf-tools.postach.io/

\section*{Sources:}

\begin{itemize}
\item JackOSX.0.92\emph{b3  to /Applications/Jack  --$>$ https://ccrma.stanford.edu/software/jacktrip/osx/JackOSX.0.92}b3.pkg
\item JMess to /usr/local/bin --$>$ https://github.com/jacktrip/jmess-jack
\item Ardour.app --$>$ https://ardour.org
\item Ultragrid --$>$ http://www.ultragrid.cz
\item TPF-TOOLS --$>$ https://gitlab.zhdk.ch/TPF
\item EMPluginSuite\_v1.11.1 --$>$ https://plugins.iem.at/
\item dearVR\emph{AMBI}MICRO.pkg --$>$ https://www.dearvr.com/products/ambi-micro
\item ICST\emph{AmbiPlugins}2.1.0\emph{osx.pkg --$>$ https://bitbucket.org/christian}schweizer/icst-ambisonics-plugins/downloads/
\end{itemize}

\hrule
License: GPL 3.0
2021@tpf-team

\end{document}
